---
title: "LME regression analyses (Analysis 1)"
author: "Jason W. Gullifer & Debra Titone"
date: '2019-07-24'
output:
  html_document:
    fig_height: 7
    fig_width: 8
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---
# Preliminaries
```{r pre, echo=F, include=F}
source("loadPackages.R")
source("utilityFunctions.R")

registerDoParallel(4)

knitr::opts_chunk$set(cache = TRUE)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(tidy = TRUE)
knitr::opts_chunk$set(fig.path='figures/analysis_1_lme4_traditional/')
knitr::opts_chunk$set(fig.show='hold')

set.seed(420)
```

# Loading exec control data
```{r}
exec_lhq<- as.data.table(fread("subjectdata/axcpt_lhq_data_forpub.csv"))
axcpt <- as.data.table(fread("rawdata/axcpt_trial_data.csv",stringsAsFactors = F, sep=","))
```

# Create folds
```{r}
k=10
k_loo = length(unique(exec_lhq$participant))

exec_lhq$participant <- as.factor(exec_lhq$participant)
exec_lhq <- fold(exec_lhq, k = k, id_col = 'participant') %>% ungroup()
exec_lhq <- fold(exec_lhq, k = k_loo, id_col = 'participant') %>% ungroup()
exec_lhq$participant <- as.numeric(as.character(exec_lhq$participant))

exec_lhq <- exec_lhq %>% 
  rename(.folds.10 = .folds_1, .folds.loo = .folds_2)
```

# Entropy PCA and scaling of variables
```{r}
exec_lhq_ppd <- preprocess_steps(exec_lhq)
```

# Join LHQ and AXCPT
```{r results='hide', warning = FALSE}
# Merge behavioral and subject data (restricting to only those in subject data frame)
axcpt_ppd <- left_join(axcpt, exec_lhq_ppd, by="participant",suffix=c(".x",""))
axcpt_ppd <- axcpt_preprocess(axcpt_ppd)

sd.rt <- axcpt_ppd %>% 
  group_by(participant) %>% 
  summarise(meanRT = mean(RT_correct,na.rm=T)) %>% 
  ungroup()

sd.acc <- axcpt_ppd %>% 
  group_by(participant) %>% 
  summarise(meanAcc=mean(accuracy_target))

sd.rt <- sd.rt %>% mutate(gmean = mean(meanRT), 
                          gsd = sd(meanRT),
                          lower = gmean - 2.5*gsd,
                          upper = gmean + 2.5*gsd,
                          outlier = ifelse(meanRT >= lower & meanRT <= upper,"fine","outlier"))

exclude <- sd.rt$participant[sd.rt$outlier=="outlier"]

axcpt_ppd <- axcpt_ppd[!(axcpt_ppd$participant %in% exclude),]

exec_lhq <- exec_lhq[!(exec_lhq$participant %in% exclude),]
exec_lhq_ppd <- exec_lhq_ppd[!(exec_lhq_ppd$participant %in% exclude),]


exec_lhq_ppd$participant <- as.factor(exec_lhq_ppd$participant)
exec_lhq_ppd <- fold(exec_lhq_ppd, k = k_loo - length(exclude), id_col = 'participant', handle_existing_fold_cols = "remove") %>% ungroup()
exec_lhq_ppd$participant <- as.numeric(as.character(exec_lhq_ppd$participant))

k_loo = k_loo - length(exclude)

exec_lhq_ppd <- exec_lhq_ppd %>% 
  rename(.folds.loo = .folds)

newfolds <- exec_lhq_ppd %>% select(participant, .folds.loo)

axcpt_ppd <- axcpt_ppd %>% select(-`.folds.loo`)
axcpt_ppd <- axcpt_ppd %>% left_join(newfolds)
```

# Jobs data
```{r}
axcpt_ppd$occupation <- factor(axcpt_ppd$occupation)
contrasts(axcpt_ppd$occupation) <- contr.sum(4)
```

# Experiment version
```{r}
axcpt_ppd$ExperimentName <- factor(axcpt_ppd$ExperimentName)
contrasts(axcpt_ppd$ExperimentName) <- contr.sum(3)
```

# Data plots
## Summary stats table

```{r}
data.agg <- exec_lhq %>% select(participant,age,
aoa,
yearsBilingual,
L1_current_exposure,
L2_current_exposure,
L3_current_exposure,
ReadEntropy,
SpeakEntropy,
HomeEntropy,
WorkEntropy,
SocialEntropy,
meanAccent,
meanL2ability)

stargazer(as.data.frame(data.agg), type="html", out="tables/summary_stats.html")
```

## Group level
```{r}
sd.rt  <- sem(axcpt_ppd, RT_correct, participant, Condition)
sd.acc <- sem(axcpt_ppd, accuracy_target, participant, Condition)

sd.rt$Condition <- factor(sd.rt$Condition, levels=c("AY","BX","BY","AX"))
sd.acc$Condition <- factor(sd.acc$Condition, levels=c("AY","BX","BY","AX"))

sd.rt$ConditionOrder <- factor(sd.rt$Condition, levels=c("AX","AY","BX","BY"))
sd.acc$ConditionOrder <- factor(sd.acc$Condition, levels=c("AX","AY","BX","BY"))

sd.rt %>% arrange(Condition)

p1 <- ggplot(sd.rt, aes(x=ConditionOrder,y=mean_RT_correct,ymin=lower,ymax=upper, fill=Condition)) +
	geom_col() + geom_errorbar(width=.2) +
	ylab("Mean RT (in ms)") + xlab("Trial type") + labs(fill="Trial type") + 
	theme_minimal(base_size = 12) + scale_fill_brewer(palette = "Set1", breaks=c("AX","AY","BX","BY"))


p2 <- ggplot(sd.acc, aes(x=ConditionOrder,y=mean_accuracy_target,ymin=lower,ymax=upper, fill=Condition)) +
	geom_col() + geom_errorbar(width=.2) +
	ylab("Mean accuracy") + xlab("Trial type") + labs(fill="Trial type") +
	theme_minimal(base_size = 12) + scale_fill_brewer(palette = "Set1", breaks=c("AX","AY","BX","BY"))

(plot <- ggarrange(p1, p2, ncol=2, labels=c("A","B"), common.legend = T, legend = "right", align = "v"))
ggsave(plot=plot, file="figures/mean_acc_rt.png", width=12, height=6, units="cm")
```

## RT: individual differences
```{r}
rt.sd <- axcpt_ppd %>% 
  group_by(participant, L2_current_exposure, aoa, PCA_General, PCA_Work, Condition) %>% 
  summarise(meanRT=mean(RT_correct, na.rm=T), 
            sdRT = sd(RT_correct, na.rm=T),
            N=n(),
            semRT = sdRT/sqrt(N))


rt.sd$Condition <- factor(rt.sd$Condition, levels=c("AY","BX","BY","AX"))

p1 <- ggplot(rt.sd, aes(x=aoa, y = meanRT, colour=Condition))+ geom_smooth(method="lm") +
  geom_point(alpha=.2) +
  ylab("Reaction time (in ms)") + xlab("L2 AoA") +
  theme_minimal(base_size = 12) + scale_colour_brewer(palette = "Set1")

p2 <- ggplot(rt.sd, aes(x=L2_current_exposure, y = meanRT, colour=Condition)) +
    geom_point(alpha=.2) +
  geom_smooth(method="lm") + ylab("Reaction time (in ms)") + xlab("L2 current exposure") +
  theme_minimal(base_size = 12) + scale_colour_brewer(palette = "Set1")

p3 <- ggplot(rt.sd, aes(x=PCA_General, y = meanRT, colour=Condition)) +
  geom_smooth(method="lm") +  geom_point(alpha=.2) +
	ylab("Reaction time (in ms)") + xlab("PC: General entropy") +
	theme_minimal(base_size = 12) + scale_colour_brewer(palette = "Set1")

p4 <- ggplot(rt.sd, aes(x=PCA_Work, y = meanRT, colour=Condition)) +
  geom_smooth(method="lm")+   geom_point(alpha=.2) +
	ylab("Reaction time (in ms)") + xlab("PC: Work entropy") +
	theme_minimal(base_size = 12) + scale_colour_brewer(palette = "Set1")


(plot <- ggarrange(p1,p2,p3,p4, nrow=2, ncol=2, labels = c("A","B","C","D"), common.legend = T, legend="right", align = "hv"))
ggsave(plot=plot, file="figures/rt_by_id.png", width=17.8, height=17.5, units="cm")
```

### RT: individual differences: raw
```{r}
raw <- axcpt_ppd[]
raw$Condition <- factor(raw$Condition, levels=c("AY","BX","BY","AX"))



p1 <- ggplot(raw, aes(x=aoa, y = RT_correct, colour=Condition))+ 
  geom_point(alpha=.05) +
  geom_smooth(method="lm") +
  ylab("Reaction time (in ms)") + xlab("L2 AoA") +
  theme_minimal(base_size = 12) + scale_colour_brewer(palette = "Set1")

p2 <- ggplot(raw, aes(x=L2_current_exposure, y = RT_correct, colour=Condition)) +
  geom_point(alpha=.05) +
  geom_smooth(method="lm") +
  ylab("Reaction time (in ms)") + xlab("L2 current exposure") +
  theme_minimal(base_size = 12) + scale_colour_brewer(palette = "Set1")

p3 <- ggplot(raw, aes(x=PCA_General, y = RT_correct, colour=Condition)) +
  geom_point(alpha=.05) +
  geom_smooth(method="lm") +  
	ylab("Reaction time (in ms)") + xlab("PC: General entropy") +
	theme_minimal(base_size = 12) + scale_colour_brewer(palette = "Set1")

p4 <- ggplot(raw, aes(x=PCA_Work, y = RT_correct, colour=Condition)) +
  geom_point(alpha=.05) +
  geom_smooth(method="lm")+   
	ylab("Reaction time (in ms)") + xlab("PC: Work entropy") +
	theme_minimal(base_size = 12) + scale_colour_brewer(palette = "Set1")


(plot <- ggarrange(p1,p2,p3,p4, nrow=2, ncol=2, labels = c("A","B","C","D"), common.legend = T, legend="right", align = "hv"))
ggsave(plot=plot, file="figures/rt_by_id_raw.png", width=17.8, height=17.5, units="cm")
 
```

## ACC: individual differences
```{r}
acc.sd <- axcpt_ppd %>% 
  group_by(participant, L2_current_exposure, aoa, PCA_General, PCA_Work, Condition) %>% 
  summarise(meanACC=mean(accuracy_target, na.rm=T), 
            sdACC = sd(accuracy_target, na.rm=T),
            N=n(),
            semACC = sdACC/sqrt(N))

p1 <- ggplot(acc.sd, aes(x=aoa, y = meanACC, colour=Condition))+ geom_smooth(method="lm") +
  geom_point(alpha=.2) +
  ylab("Mean accuracy") + xlab("L2 AoA") +
  theme_minimal(base_size = 12) + scale_colour_brewer(palette = "Set1")

p2 <- ggplot(acc.sd, aes(x=L2_current_exposure, y = meanACC, colour=Condition)) +
    geom_point(alpha=.2) +
  geom_smooth(method="lm") + ylab("Mean accuracy") + xlab("L2 current exposure") +
  theme_minimal(base_size = 12) + scale_colour_brewer(palette = "Set1")

p3 <- ggplot(acc.sd, aes(x=PCA_General, y = meanACC, colour=Condition)) +
  geom_smooth(method="lm") +  geom_point(alpha=.2) +
	ylab("Mean accuracy") + xlab("PC: General entropy") +
	theme_minimal(base_size = 12) + scale_colour_brewer(palette = "Set1")

p4 <- ggplot(acc.sd, aes(x=PCA_Work, y = meanACC, colour=Condition)) +
  geom_smooth(method="lm")+   geom_point(alpha=.2) +
	ylab("Mean accuracy") + xlab("PC: Work entropy") +
	theme_minimal(base_size = 12) + scale_colour_brewer(palette = "Set1")


(plot <- ggarrange(p1,p2,p3,p4, nrow=2, ncol=2, labels = c("A","B","C","D"), common.legend = T, legend="right", align = "hv"))
ggsave(plot=plot, file="figures/acc_by_id.png", width=17.8, height=17.5, units="cm")

```


# Set loo fold
```{r}
axcpt_ppd$.folds <- axcpt_ppd$.folds.loo
axcpt_ppd <- axcpt_ppd[axcpt_ppd$Condition!="AX",]
```

# Traditional AXCPT analysis 
```{r}


mod.rt.0  <- "RT_correct  ~  Condition + (1|participant)"

mod.rt.1  <- "RT_correct  ~  Condition*aoa + Condition*L2_exposure +  (1|participant)"

mod.rt.1.1  <- "RT_correct  ~  Condition*PCA_Work + Condition*PCA_General +  (1|participant)"

mod.rt.2  <- "RT_correct  ~  Condition*aoa + Condition*L2_exposure + Condition*PCA_Work + Condition*PCA_General +  (1|participant)"

mod.rt.3  <- "RT_correct  ~  aoa * (Condition*L2_exposure + Condition*PCA_Work + Condition*PCA_General) +  (1|participant)"



mod.acc.0  <- "acc        ~   Condition + (1|participant)"

mod.acc.0.1  <- "acc        ~   Condition + L2_exposure*aoa + (1|participant)"

mod.acc.1  <- "acc        ~   Condition*aoa + Condition*L2_exposure + (1|participant)"

mod.acc.1.1  <- "acc        ~   Condition*PCA_Work + Condition*PCA_General + (1|participant)"

mod.acc.2  <- "acc        ~   Condition*aoa + Condition*L2_exposure + Condition*PCA_Work + Condition*PCA_General + (1|participant)"

mod.acc.3  <- "acc        ~   aoa * (Condition*L2_exposure + Condition*PCA_Work + Condition*PCA_General) + (1|participant)"


```

## RT models
```{r}
#axcpt_ppd <- axcpt_ppd[!(axcpt_ppd$participant %in% exclude),]
axcpt_ppd$Condition<-relevel(axcpt_ppd$Condition, ref="BX")
all.rt.0    <- lmer(mod.rt.0, axcpt_ppd, REML=F)
all.rt.1    <- lmer(mod.rt.1, axcpt_ppd, REML=F)
all.rt.1.1  <- lmer(mod.rt.1.1, axcpt_ppd, REML=F)
all.rt.2    <- lmer(mod.rt.2, axcpt_ppd, REML=F)
all.rt.3    <- lmer(mod.rt.3, axcpt_ppd, REML=F)
```

```{r}
anova(all.rt.0, all.rt.1, all.rt.2, all.rt.3)
```

```{r}
kable(anova(all.rt.0, all.rt.1, all.rt.2, all.rt.3))
kable(anova(all.rt.0, all.rt.1.1, all.rt.2, all.rt.3))
```


```{r}
AIC(all.rt.0, all.rt.1, all.rt.1.1, all.rt.2, all.rt.3)
BIC(all.rt.0, all.rt.1, all.rt.1.1, all.rt.2, all.rt.3)
```
So entropy explains more then L2 exp and aoa but not vice versa

```{r}
summ(all.rt.1.1, confint=T, digits=3)
summary(all.rt.1.1)
anova(all.rt.1.1)
```

```{r}
ef<-	as.data.frame(Effect(c("PCA_Work","Condition"),all.rt.1.1, xlevels=list(PCA_Work=c(-2,-1,0,1,2)),
													confidence.level = .686))

f1a <- ggplot(ef, aes(x=PCA_Work, y=fit, ymin=lower,ymax=upper,group=Condition))	+  
	geom_line(aes(colour=Condition), size=1) + geom_ribbon(fill="grey", alpha=.3) +
	coord_cartesian(ylim=c(300,550)) +
	ylab("Model-estimated\nreaction time (in ms)") + xlab("PC: Work Entropy") +
		scale_colour_brewer(palette = "Set1") + theme_bw(base_size=12) + 
  labs(color="Trial type") + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

#ggsave("figures/axcpt_rt_work_condition.png", width=8.9, height=6, units = "cm")

ef<-	as.data.frame(Effect(c("PCA_General","Condition"),all.rt.1.1, xlevels=list(PCA_General=c(-2,-1,0,1,2)),
													confidence.level = .686))

f1b <- ggplot(ef, aes(x=PCA_General, y=fit, ymin=lower,ymax=upper,group=Condition))	+  
	geom_line(aes(colour=Condition), size=1) + geom_ribbon(fill="grey", alpha=.3) +
	coord_cartesian(ylim=c(300,550)) +
	ylab("Model-estimates\nreaction time (in ms)") + xlab("PC: General Entropy") +
  labs(color="Trial type") +
		scale_colour_brewer(palette = "Set1") + theme_bw(base_size = 12) + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

#ggsave("figures/axcpt_rt_general_condition.png", width=8.9, height=6, units = "cm")

(f1 <- ggarrange(f1b,f1a, labels=c("A","B"), legend="bottom", common.legend = T))

ggsave(plot = f1, "figures/traditional_rt_lme4_effects.png", width=17.8, height=8, units = "cm")
```

## RT models cross validated
```{r}
cv.all.rt.0    <- crossvalidate(mod=mod.rt.0, k=k_loo,    data=axcpt_ppd,
                                dependent='RT_correct', dv_continuous=T, random=TRUE,
                                returnRuns = T)

cv.all.rt.1    <- crossvalidate(mod=mod.rt.1, k=k_loo,    data=axcpt_ppd,
                                dependent='RT_correct', dv_continuous=T, random=TRUE,
                                returnRuns = T)

cv.all.rt.1.1  <- crossvalidate(mod=mod.rt.1.1, k=k_loo,  data=axcpt_ppd,
                                dependent='RT_correct', dv_continuous=T, random=TRUE,
                                returnRuns = T)

cv.all.rt.2    <- crossvalidate(mod=mod.rt.2, k=k_loo,    data=axcpt_ppd,
                                dependent='RT_correct', dv_continuous=T, random=TRUE,
                                returnRuns = T)

cv.all.rt.3    <- crossvalidate(mod=mod.rt.3, k=k_loo,    data=axcpt_ppd,
                                dependent='RT_correct', dv_continuous=T, random=TRUE,
                                returnRuns = T)



cv.rt.0.iter = cv.all.rt.0$performances
cv.rt.0      = cv.all.rt.0$performances_mean

cv.rt.1.iter = cv.all.rt.1$performances
cv.rt.1      = cv.all.rt.1$performances_mean

cv.rt.1.1.iter = cv.all.rt.1.1$performances
cv.rt.1.1      = cv.all.rt.1.1$performances_mean

cv.rt.2.iter = cv.all.rt.2$performances
cv.rt.2      = cv.all.rt.2$performances_mean

cv.rt.3.iter = cv.all.rt.3$performances
cv.rt.3      = cv.all.rt.3$performances_mean
```

```{r}
xval_axcpt_rt_k_loo.iter <- rbind.data.frame(cv.rt.0.iter, cv.rt.1.iter, 
                                             cv.rt.1.1.iter, cv.rt.2.iter, cv.rt.3.iter)
write.csv(xval_axcpt_rt_k_loo.iter, "tables/xval_axcpt_rt_k_loo.iter.csv", row.names=F)

xval_axcpt_rt_k_loo.iter <- xval_axcpt_rt_k_loo.iter %>% 
  group_by(mod) %>% 
  mutate(meanRMSE_test = mean(RMSE_test)) %>% 
  ungroup() %>% 
  mutate(mod = fct_reorder(mod, desc(meanRMSE_test)))

mean.xval_axcpt_rt_k_loo.iter <- xval_axcpt_rt_k_loo.iter %>% 
  group_by(mod) %>% 
  summarise(meanRMSE_train = mean(RMSE_train),
            meanRMSE_test = mean(RMSE_test),
            meanr2_train = mean(r2_train),
            meanr2_test = mean(r2_test),
            sd = sd(RMSE_test),
            N=n(),
            sem=sd/sqrt(N)) %>% 
  ungroup() %>%
  mutate(mod=fct_reorder(mod, desc(meanRMSE_test)))

write.csv(mean.xval_axcpt_rt_k_loo.iter, "tables/xval_axcpt_rt_k_loo.mean.csv", row.names=F)


```

## ACC models
```{r}
all.acc.0    <- glmer(mod.acc.0,   axcpt_ppd,
                   family="binomial", control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=3e5)))

all.acc.0.1    <- glmer(mod.acc.0.1,   axcpt_ppd,
                   family="binomial", control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=3e5)))

all.acc.1    <- glmer(mod.acc.1,   axcpt_ppd,
                   family="binomial", control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=3e5)))

all.acc.1.1  <- glmer(mod.acc.1.1, axcpt_ppd,
                   family="binomial", control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=3e5)))

all.acc.2    <- glmer(mod.acc.2,  axcpt_ppd,
                   family="binomial", control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=3e5)))

all.acc.3    <- glmer(mod.acc.3,  axcpt_ppd,
                   family="binomial", control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=3e5)))
```


```{r}
kable(anova(all.acc.0, all.acc.1, all.acc.2, all.acc.3))
kable(anova(all.acc.0, all.acc.1.1, all.acc.2, all.acc.3))
kable(anova(all.acc.0, all.acc.0.1))
```


```{r}
summ(all.acc.0.1, confint=T, digits=3)
summ(all.acc.0, confint=T, digits=3)
anova(all.acc.0)
```


```{r}
ef<-	as.data.frame(Effect(c("L2_exposure","aoa"),all.acc.0.1, xlevels=list(aoa=c(-2,-1,0,1,2)),
                          confidence.level = .686))
ef$aoa <- factor(ef$aoa)
f_acc <- ggplot(ef, aes(x=L2_exposure, y=fit, ymin=lower,ymax=upper,group=aoa))	+  
  geom_line(aes(colour=aoa), size=1) + geom_ribbon(fill="grey", alpha=.3) +
  coord_cartesian(ylim=c(.5,1)) +
  ylab("Model-estimated\naccuracy") + xlab("Scaled L2 exposure") +
  scale_colour_brewer(palette = "Dark2") + theme_bw(base_size=12) + theme(panel.border = element_blank(), panel.grid.major = element_blank(),
                                                                          panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

ggsave("figures/traditional_acc_plot.png", plot = f_acc, width=12, height=8, units = "cm")

```


<!--## ACC models cross validated-->
```{r eval=FALSE, include=FALSE}
# This code is not run in rmarkdown form. Takes hours then hangs at 100%.

cv.all.acc.0    <- crossvalidate(mod=mod.acc.0, k=k_loo,    data=axcpt_ppd,
                                 dependent='acc', dv_continuous=F, random=TRUE,
                                 returnRuns = T)

cv.all.acc.0.1    <- crossvalidate(mod=mod.acc.0.1, k=k_loo,    data=axcpt_ppd,
                                   dependent='acc', dv_continuous=F, random=TRUE,
                                   returnRuns = T)

cv.all.acc.1    <- crossvalidate(mod=mod.acc.1, k=k_loo,    data=axcpt_ppd,
                                 dependent='acc', dv_continuous=F, random=TRUE,
                                 returnRuns = T)

cv.all.acc.1.1  <- crossvalidate(mod=mod.acc.1.1, k=k_loo,  data=axcpt_ppd,
                                 dependent='acc', dv_continuous=F, random=TRUE,
                                 returnRuns = T)

cv.all.acc.2    <- crossvalidate(mod=mod.acc.2, k=k_loo,    data=axcpt_ppd,
                                 dependent='acc', dv_continuous=F, random=TRUE,
                                 returnRuns = T)

cv.all.acc.3    <- crossvalidate(mod=mod.acc.3, k=k_loo,    data=axcpt_ppd,
                                 dependent='acc', dv_continuous=F, random=TRUE,
                                 returnRuns = T)



cv.acc.0.iter = cv.all.acc.0$performances
cv.acc.0      = cv.all.acc.0$performances_mean

cv.acc.0.1.iter = cv.all.acc.0.1$performances
cv.acc.0.1      = cv.all.acc.0.1$performances_mean

cv.acc.1.iter = cv.all.acc.1$performances
cv.acc.1      = cv.all.acc.1$performances_mean

cv.acc.1.1.iter = cv.all.acc.1.1$performances
cv.acc.1.1      = cv.all.acc.1.1$performances_mean

cv.acc.2.iter = cv.all.acc.2$performances
cv.acc.2      = cv.all.acc.2$performances_mean

cv.acc.3.iter = cv.all.acc.3$performances
cv.acc.3      = cv.all.acc.3$performances_mean

xval_axcpt_acc_k_loo.iter <- rbind.data.frame(cv.acc.0.iter, cv.acc.0.1.iter, cv.acc.1.iter, 
                                              cv.acc.1.1.iter, cv.acc.2.iter, cv.acc.3.iter)
write.csv(xval_axcpt_acc_k_loo.iter, "tables/xval_axcpt_acc_k_loo.iter.csv", row.names=F)

### FIX BELOW

xval_axcpt_acc_k_loo.iter <- xval_axcpt_acc_k_loo.iter %>% 
  group_by(mod) %>% 
  mutate(meanAUC_test = mean(auc_test,na.rm=T),
         meanError_test = mean(error_test)) %>% 
  ungroup() %>% 
  mutate(mod = fct_reorder(mod, desc(meanAUC_test)))

mean.xval_axcpt_acc_k_loo.iter <- xval_axcpt_acc_k_loo.iter %>% 
  group_by(mod) %>% 
  summarise(meanError_train = mean(error_train),
            meanError_test = mean(error_test),
            meanAUC_train = mean(auc_train),
            meanAUC_test = mean(auc_test,na.rm=T), 
            sdError_test = sd(error_test),
            sdAUC_test = sd(auc_test,na.rm=T),
            N=n(),
            semError=sdError_test/sqrt(N),
            semAUC = sdError_test/sqrt(N)) %>% 
  ungroup() %>%
  mutate(mod=fct_reorder(mod, desc(meanAUC_test)))

write.csv(mean.xval_axcpt_acc_k_loo.iter, "tables/xval_axcpt_acc_k_loo.mean.csv", row.names=F)
```
